---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
library(extrafont)
library(ecorys)
data("mtcars")
```

# ecorys R package

`ecorys` is a package of tools for working with R at Ecorys. It is currently under development and will likely be updated with new functions in the future.

## Installation and updating

You can install the latest version of `ecorys` by running the following code in your R console. If you have already installed `ecorys` and want to update the package to the latest version, you can also use the following code.

``` r
if (!require(devtools)) {
    install.packages('devtools')
}
devtools::install_github("j-lillis/ecorys")
```

## Features

Currently `ecorys` provides the following tools which are designed to make it easy to format `ggplot2` plots in Ecorys branding:

-   `theme_ecorys()` - add this to your plot to format it in Ecorys style

-   `ecorys_colours` - a list of Ecorys brand colours. Use `$` to access individual colours, e.g. `ecorys_colours$blue`

-   `ecorys_palettes` - a list of palettes, each composed of Ecorys brand colours. Use `$` to access palettes, e.g. `ecorys_palettes$primary`

`ecorys` is also being updated with functions to support wrangling and cleaning data. Currently it contains the following function:

-   `fct_case_when()` - an extension of `dplyr::case_when` which outputs right hand side values as factors, where the order of resulting factor levels reflects the order in which arguments to the function are specified.

## Examples

Using `theme_ecorys()` and accessing colours from `ecorys_colours`.

Note the arguments specified to `theme_ecorys()` to display y-axis grid lines and main axis lines.

```{r}
mtcars %>% 
  ggplot(aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 4, alpha = 0.8) +
  scale_colour_manual(values = c(ecorys_colours$blue, 
                                 ecorys_colours$purple, 
                                 ecorys_colours$green),
                      name = "Cylinders:") +
  labs(title = "Plot using Ecorys theme") +
  ylab("Miles/(US) gallon") +
  xlab("Displacement (cu.in.)") +
  theme_ecorys(grid.major.y = TRUE,
               axis.line = TRUE)
```

As above, but using `facet_wrap()`. Note that within `theme_ecorys()`, `strip.background` can be set to `FALSE` to remove the grey boxes surrounding facet titles.

```{r}
mtcars %>%
  ggplot(aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 4, alpha = 0.8) +
  scale_colour_manual(values = c(ecorys_colours$blue, 
                                 ecorys_colours$purple, 
                                 ecorys_colours$green),
                      name = "Cylinders:") +
  labs(title = "Plot using Ecorys theme and facets") +
  ylab("Miles/(US) gallon") +
  xlab("Displacement (cu.in.)") +
  facet_wrap(~cyl) +
  theme_ecorys(grid.major.y = TRUE) +
  theme(legend.position = "none")

```
